Geometric variational problems

### 2020-11-10 NSF2020/Description/background.tex
working on background but not done yet

\subsection{Hydrophobic Attraction Potential (HAP)}
\label{sec:HAP}
%Based on the physical origin of hydrophobicity,  we have devised a
%functional, called the hydrophobic attraction potential (HAP), to model
%hydrophobic forces~\cite{Fu2018_SIAM}. 
The motivation for the HAP concept
stemmed from PI RR's earlier work on the problem of energy barriers in
membrane fusion~\cite{RyKlYaCo16,Chetal16}.  There, PI RR and
collaborators resolved the long-standing issue of accounting for the
energy of a fissure surface during topological transitions, by applying
a squared gradient mathematical theory for hydrophobic attraction
between planar surfaces~\cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer
fissures.  Based on PI RR and YNY's coarse-grained membrane modeling
work \cite{Fu2017}, the investigators initiated a collaboration to
create a gradient theory for arbitrary collections of hydrophobic and
amphiphilic particles. This new method eliminates the costly calculation
of water by treating the solvent implicitly, and avoids complicated
re-meshing schemes of continuum approaches by utilizing a particle-based
representation.

To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  
modeling the solvent surrounding a number of particles (Figure \ref{fig:domain}).
As stated earlier, the HAP must be an energy of the shape of the region
because hydrophobic attraction is non-additive. 
The boundary of the region is the water-particle interface and some parts of this
surface are hydrophobic while others are hydrophilic. 
Monte Carlo simulations 
show that water changes structure at hydrophobic interfaces \cite{Luzar1987, Jonsson2006,Varilly2011}.
Due to rapid fluctuation in the hydrogen bond network,
restructuring at the interface extends into bulk water.
This motivates the following definition for the HAP of the particles:
\begin{equation}
\label{HAP}
  \Phi = \gamma \iiint_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,dx \,dy \,dz, 
\end{equation}
where $u$ is the unique solution of screened Laplace equation boundary value problem 
\begin{equation}
  \label{SL}
  -\rho^2 \Delta u + u = 0 \in \Omega,\quad u = f  \mbox{ on } \partial \Omega, \quad u(x) \to 0 \mbox{ as } x \to \infty.
\end{equation}
The scalar function $u(x)$ is called the water activity. Its boundary values $f$ 
define the degree of hydrophobicity of the water-particle interface. The value 
1 represents a completely hydrophobic interface, where water has lost rotational freedom. 
Conversely, the boundary value 0 corresponds to a polar surface where water has the same rotational
freedom as in bulk water. The parameter $\rho$ is the decay length of attraction, 
around 1 nm, and the parameter $\gamma$ is the interfacial tension \cite{Israelachvili1954}.
The parameters $\rho$ and $\gamma$ contain information about the quality
of the solvent \cite{Discher2002}.

From a phenomenological perspective, (\ref{HAP}--\ref{SL}) 
is an appropriate model of hydrophobic attraction. Specifically,
using boundary layer analysis, it is possible 
to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g.~between hydrophobic parallel disks
separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
derived from HAP theory are non-additive, and even deviate significantly from 
a pairwise potential \cite{Meyer2006,Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

%As a summary of its mathematical properties,  the hydrophobic force
%is a non-additive, exponentially decaying surface force 
%that possesses a separation of length scales. These properties suggest 
%a boundary value problem formulation of the hydrophobic force.  
%The non-additivity of the hydrophobic force has to do with the fact that there is no superposition
%principle for including subdomains in boundary value problems. 
%The exponential decay is a property of a second order elliptic partial differential equation (PDE). 
%Finally, the separation of scales come from boundary layers, 
%where the energy of the boundary layer in the zero-thickness limit corresponds to macroscopic interfacial tension.
%Overlapping boundary layers correspond to microscopic hydrophobic attraction, 
%and the boundary layer thickness corresponds to the decay length of attraction.
%
%
%\section{Previous Results by the PIs}
%\label{sec:results}
%
%%In our paper \cite{Fu2018_SIAM}, 
%PIs RR and YNY developed the HAP model (\ref{HAP}--\ref{SL})
%to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents \cite{Fu2018_SIAM}.
%%We formulated the boundary value problem as a second-kind
%%integral equation (SKIE), presented in the Section (). 
%%The simulated fluid-particle systems exhibit a variety of multiscale behaviors over both time and length.
%%Over short time scales, the numerical results showed self-assembly for model lipid particles. 
%%For large system simulations, the particles formed realistic configurations like micelles and bilayers. 
%%Our collections showed that these amphiphilic particle bilayers  possessed mechanical properties of a 
%%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
To define the particle dynamics, consider the exterior domain $\Omega$
for a finite number of disjoint, rigid and closed particles $P_1$, $P_2$, \dots, $P_n$, each with Lipschitz boundary,
and boundary data $f$ in the Sobolev space $H^1(\Omega).$ 
For any fixed configuration, the functional \eqref{HAP} has a unique minimizer $u$
among all $u - f$ with vanishing trace. This minimizer is a solution to \eqref{SL}.
Conversely, from maximum principles and energy estimates,  any solution of 
\eqref{SL} is the minimizer of \eqref{HAP}, and this supplies $\Phi$ with a well-defined value.

Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
in a critical way,
%leads to the surface term \eqref{stress}.  
the first variation of the hydrophobic potential $\Phi$  
yields a symmetric, rank-two tensor \cite{Bandle2015,Schiffer1954,Grinfeld2010} called the hydrophobic stress:
\begin{equation}
  \label{stress}
\boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho \gamma (\tfrac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T).
\end{equation}
%
%To obtain \eqref{stress}, we observe that the potential $\Phi$ is a function of the particle position and orientations.
%This is because the particle configuration defines the shape of $\Omega$ and the boundary data $f.$ 
%Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
%in a critical way leads to the surface term \eqref{stress}.  
%
By integrating the hydrophobic stress over the surface of particle $P_i,$ we obtaining the hydrophobic force and torque on each particle 
\begin{equation}
  \label{forceandtorque}
  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n} \,dS,\quad
  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.
\end{equation}
We verified that this system is force and torque free.
To supply viscous dissipation, 
we incorporated the mobility problem in Stokes flow to obtain the rigid body motions; 
\begin{equation}
\label{eq:stokes}
\begin{aligned}
&-\mu \Delta {\bf u} + \nabla p = 0, \quad \text{in}\ \Omega, \qquad 
\nabla \cdot {\bf u} = 0,  \quad \text{in}\ \Omega,\\
&{\bf u}({\bf x}) \to 0 \quad \text{as}\ |{\bf x}|\to \infty,\qquad 
  \mathbf{u}(\mathbf{x})|_{\partial P_i} = \mathbf{v}_i +
\boldsymbol{\omega}_i\times(\mathbf{x} - \mathbf{a}_i),\\
&\int_{\partial P_i}\boldsymbol{\sigma}\cdot {\bf n} dS=-{\bf F}_i, \quad
\int_{\partial P_i}(\mathbf{x}-\mathbf{a}_i)\times (\boldsymbol{\sigma} \cdot \mathbf{n}) dS=-{\bf T}_i.
\end{aligned}
\end{equation}
Here $\mu$ is the fluid viscosity and the first two equations state
that the fluid motion is a
divergence-free Stokes flow; the third equation specifies the fluid
velocity at infinity;
the fourth equation enforces a rigid body motion constraint on each
particle, where
$\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
angular velocities
of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of $P_i$;
the last two equations state that the net forces and torques
on each particle are given by the quantities ${\bf F}_i$ and ${\bf T}_i$
from \eqref{forceandtorque}, and $\boldsymbol{\sigma}$ is the fluid shear stress.

The time integration of particle configurations goes as follows: 
\textbf{(i)} solve the BVP \eqref{SL} for the screened Laplace equation, 
\textbf{(ii)} determine the rigid body forces and torques \eqref{forceandtorque}, 
\textbf{(iii)} solve the Stokes mobility problem \eqref{eq:stokes} for rigid body motion,
\textbf{(iv)} update the particle configuration. 
\S \ref{subsec:specific_aim_2}, addresses the numerical challenges in 
evaluating \eqref{stress} and how these challenges are overcome.

@@

Our simulations used Janus particles to model
lipid amphiphiles. Janus particles are a popular tool in material science and physics
for creating functional materials \cite{Lee2014, Lee2013}. 
%This topic is the basis of Specific Aim 3 \todo[inline]{not true anymore}. 
Janus particles are typically
spherical with a biphasic material label on either hemisphere,  endowing the particle
with a directional order. We considered a two-dimensional system, and represented an 
elongated lipid by elliptical particles with hydrophobic and hydrophilic labels along the ellipse's long axis.

Under the hydrophobic force, and with an excluded volume to prevent collisions, the 
Janus particles spontaneously merge and realign to form bilayers. This occurs only as a result
of energy minimization and does not require artificial inputs. To our knowledge, this is the first demonstration 
of bilayer self-assembly by a continuum hydrophobic interaction model \cite{Noguchi2001,Farago2003,Brannigan2006,Brooks2009,Wang2013}.

It is worth emphasizing that the HAP model uses only a few parameters; interfacial tension, decay length, repulsion strength and particle
shape. For example, an elastic modulus for stretching a vesicle from micropipette manipulation 
directly calibrate our interfacial tension parameter. This is in direct contrast with pair-potential based approaches in
MD simulations and coarse-grained models where many more parameters are required \cite{Varilly2011,Wang2013}.
%MD simulators have also made measurements and lately there is better and better agreement with reality. 
%But even the simplest coarse grained models based on pair potentials for lipids has many more parameters \cite{Varilly2011,Wang2013} .

@@

Our HAP approach differs from prior methods in a number of respects. 
First, we do not assume a surface. Rather, we more fundamentally  consider a collection of amphiphilic particles.
The collection of amphiphiles minimize hydrophobic interactions by sequestering hydrophobic tails in the form of a bilayer, and the particles' excess free energy gives rise to an elastic bilayer energy. 
The second difference lies in the fluid-interface coupling. Here, the associated mobility problem \eqref{eq:stokes} 
is more complicated than dealing with a stress boundary condition or diffusive surface force, 
because the fluid velocity must be that of a rigid body motion at the particle surfaces.
%
\begin{wrapfigure}[17]{l}{0.4\textwidth}
\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
\caption{\label{fig:demixing} An initial assembly of small and 
large particles spontaneous segregates into two smaller bodies. }
\end{wrapfigure}
The greatest strength of using HAP to model lipid bilayer membrane is the ability
to form discontinuities (interfacial singularity) from first physical principle without any artificial manipulation to rearrangement the interface.
%The ability to form discontinuities is perhaps the HAP method's greatest strength.
For example, using the HAP model to simulate a vesicle under a shear flow that is strong enough to cause the vesicle membrane to rupture, 
we expect the HAP model to capture the reorganization of lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which is a nearly impossible
task using phase-field or immerse boundary method without extreme refinement around the membrane and artificial treatment of reconnection during the topological change of an interface.

>>>>

\subsection{Hydrophobic Attraction Potential (HAP)}
\label{sec:HAP}
%Based on the physical origin of hydrophobicity,  we have devised a
%functional, called the hydrophobic attraction potential (HAP), to model
%hydrophobic forces~\cite{Fu2018_SIAM}. 
The motivation for the HAP concept stemmed from PI RR's earlier work on
the problem of energy barriers in membrane
fusion~\cite{RyKlYaCo16,Chetal16}. By applying a squared gradient
mathematical theory for hydrophobic attraction between planar
surfaces~\cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977}, PI RR
and collaborators resolved the long-standing issue of accounting for the
energy of a monolayer fissure surface during topological transitions.
Based on PI RR and YNY's coarse-grained membrane modeling
work~\cite{Fu2017}, the investigators initiated a collaboration to
create a gradient theory for arbitrary collections of hydrophobic and
amphiphilic particles. This new method eliminates the costly calculation
of water by treating the solvent implicitly, and avoids complicated
re-meshing schemes of continuum approaches by utilizing a particle-based
representation.

To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  modeling
the solvent surrounding a number of particles (Figure \ref{fig:domain}).
The HAP must be an energy of the shape of the region because hydrophobic
attraction is non-additive. The boundary of the region is the
water-particle interface and some parts of this surface are hydrophobic
while others are hydrophilic. Monte Carlo simulations show that water
changes structure at hydrophobic interfaces~\cite{Luzar1987,
Jonsson2006, Varilly2011}. Due to rapid fluctuation in the hydrogen bond
network, restructuring at the interface extends into bulk water. This
motivates the following definition for the HAP of the particles:
\begin{align}
\label{HAP}
  \Phi = \gamma \iiint_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,dx \,dy \,dz, 
\end{align}
where $u$ is the unique solution of the screened Laplace equation boundary value problem 
\begin{equation}
  \label{SL}
  -\rho^2 \Delta u + u = 0, \mbox{ } x \in \Omega, \qquad
  u = f,  \mbox{ } x \in \partial \Omega, \qquad 
  u(x) \to 0 \mbox{ as } |x| \to \infty.
\end{equation}
The scalar function $u(x)$ is called the water activity. Its boundary
values $f$ define the degree of hydrophobicity of the water-particle
interface. If $f=1$, the interface is hydrophobic and water has lost
rotational freedom. Conversely, if $f=0$, the interface has the same
rotational freedom as in bulk water. The parameter $\rho$ is the decay
length of attraction, around 1 nm, and the parameter $\gamma$ is the
interfacial tension~\cite{Israelachvili1954}. Both parameters contain
information about the quality of the solvent~\cite{Discher2002}.

From a phenomenological perspective, equations~\eqref{HAP}
and~\eqref{SL} is an appropriate model of hydrophobic attraction.
Specifically, using boundary layer analysis, it is possible to show that
$\Phi$ converges to a surface energy in the zero-decay length
limit~\cite{Lee2018, Lin2015, Shibata2004}. For non-zero decay lengths,
solutions of~\eqref{SL} yield an attractive interaction between
hydrophobic parallel disks separated by water~\cite{Eriksson1989}. Also,
we have demonstrated with simulation that the forces derived from HAP
theory are non-additive and significantly deviate from a pairwise
potential~\cite{Meyer2006, Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

%As a summary of its mathematical properties,  the hydrophobic force
%is a non-additive, exponentially decaying surface force 
%that possesses a separation of length scales. These properties suggest 
%a boundary value problem formulation of the hydrophobic force.  
%The non-additivity of the hydrophobic force has to do with the fact that there is no superposition
%principle for including subdomains in boundary value problems. 
%The exponential decay is a property of a second order elliptic partial differential equation (PDE). 
%Finally, the separation of scales come from boundary layers, 
%where the energy of the boundary layer in the zero-thickness limit corresponds to macroscopic interfacial tension.
%Overlapping boundary layers correspond to microscopic hydrophobic attraction, 
%and the boundary layer thickness corresponds to the decay length of attraction.
%\section{Previous Results by the PIs}
%\label{sec:results}
%%In our paper \cite{Fu2018_SIAM}, 
%PIs RR and YNY developed the HAP model (\ref{HAP}--\ref{SL})
%to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents \cite{Fu2018_SIAM}.
%%We formulated the boundary value problem as a second-kind
%%integral equation (SKIE), presented in the Section (). 
%%The simulated fluid-particle systems exhibit a variety of multiscale behaviors over both time and length.
%%Over short time scales, the numerical results showed self-assembly for model lipid particles. 
%%For large system simulations, the particles formed realistic configurations like micelles and bilayers. 
%%Our collections showed that these amphiphilic particle bilayers  possessed mechanical properties of a 
%%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
To define the particle dynamics, consider the exterior domain $\Omega$
for a finite number of disjoint, rigid and closed particles $P_1$,
$P_2$, \ldots, $P_n$, each with Lipschitz boundary, and boundary data
$f$ in the Sobolev space $H^1(\Omega)$. For any fixed configuration, the
minimizer of the functional~\eqref{HAP} among all $u - f$ with vanishing
trace is the solution of~\eqref{SL}. Conversely, from maximum principles
and energy estimates, any solution of~\eqref{SL} is the minimizer
of~\eqref{HAP}, and this supplies $\Phi$ with a well-defined value.
Taking the derivative of~\eqref{HAP} with respect to particle
configurations, and using the boundary value problem~\eqref{SL}, the
first variation of the hydrophobic potential $\Phi$ yields a symmetric,
rank-two tensor~\cite{Bandle2015, Schiffer1954, Grinfeld2010} called the
hydrophobic stress:
\begin{align}
  \label{stress}
\boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho \gamma (\tfrac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T).
\end{align}
%To obtain \eqref{stress}, we observe that the potential $\Phi$ is a function of the particle position and orientations.
%This is because the particle configuration defines the shape of $\Omega$ and the boundary data $f.$ 
%Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
%in a critical way leads to the surface term \eqref{stress}.  
Integrating the hydrophobic stress over the surface of particle $P_i$
reveals the hydrophobic force and torque on each particle 
\begin{align}
  \label{forceandtorque}
  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n} \,dS,\quad
  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.
\end{align}
Our previous verifies that this system is force- and torque-free and
\S\ref{subsec:specific_aim_2} addresses the numerical challenges in
evaluating~\eqref{stress} and how these challenges are overcome. To
supply viscous dissipation, we incorporated the mobility problem in
Stokes flow to obtain the rigid body motions:
\begin{equation}
\label{eq:stokes}
\begin{aligned}
&-\mu \Delta {\bf u} + \nabla p = 0, \quad \text{in}\ \Omega, \qquad 
\nabla \cdot {\bf u} = 0,  \quad \text{in}\ \Omega,\\
&{\bf u}({\bf x}) \to 0 \quad \text{as}\ |{\bf x}|\to \infty,\qquad 
  \mathbf{u}(\mathbf{x})|_{\partial P_i} = \mathbf{v}_i +
\boldsymbol{\omega}_i\times(\mathbf{x} - \mathbf{a}_i),\\
&\int_{\partial P_i}\boldsymbol{\sigma}\cdot {\bf n} dS=-{\bf F}_i, \quad
\int_{\partial P_i}(\mathbf{x}-\mathbf{a}_i)\times (\boldsymbol{\sigma} \cdot \mathbf{n}) dS=-{\bf T}_i.
\end{aligned}
\end{equation}
Here $\mu$ is the fluid viscosity and the first two equations state that
the fluid motion is a divergence-free Stokes flow; the third equation
specifies the fluid velocity at infinity; the fourth equation enforces a
rigid body motion constraint on each particle, where $\mathbf{v}_i$ and
$\boldsymbol{\omega}_i$ are unknown translation and angular velocities
of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of
$P_i$; the last two equations state that the net forces and torques on
each particle are ${\bf F}_i$ and ${\bf T}_i$
from~\eqref{forceandtorque}, respectively, and $\boldsymbol{\sigma}$ is
the fluid shear stress. The time integration of particle configurations
goes as follows: \textbf{(i)} solve the BVP~\eqref{SL} for the screened
Laplace equation, \textbf{(ii)} determine the rigid body forces and
torques~\eqref{forceandtorque}, \textbf{(iii)} solve the Stokes mobility
problem~\eqref{eq:stokes} for rigid body motion, \textbf{(iv)} update
the particle configuration. Numerical challenges and how these
challenges are overcome are described in \S\ref{subsec:specific_aim_2}.

@@

Our simulations use Janus particles to model lipid amphiphiles which are
popular in material science and physics for creating functional
materials~\cite{Lee2014, Lee2013}. Janus particles are typically
spherical with a biphasic material label on either hemisphere, endowing
the particle with a directional order. We considered a two-dimensional
system, and represented an elongated lipid by elliptical particles with
hydrophobic and hydrophilic labels along the ellipse's long axis. Under
the hydrophobic force, and with an excluded volume to prevent
collisions, the Janus particles spontaneously merge and realign to form
bilayers. This occurs only as a result of energy minimization and does
not require artificial inputs. To our knowledge, this is the first
demonstration of bilayer self-assembly by a continuum hydrophobic
interaction model~\cite{Noguchi2001, Farago2003, Brannigan2006,
Brooks2009, Wang2013}.

It is worth emphasizing that the HAP model uses only a few parameters;
interfacial tension, decay length, repulsion strength, and particle
shape. For example, an elastic modulus for stretching a vesicle from
micropipette manipulation directly calibrate our interfacial tension
parameter. This is in direct contrast with pair-potential based
approaches in MD simulations and coarse-grained models where many more
parameters are required~\cite{Varilly2011, Wang2013}.
%MD simulators have also made measurements and lately there is better and better agreement with reality. 
%But even the simplest coarse grained models based on pair potentials for lipids has many more parameters \cite{Varilly2011,Wang2013} .

@@

Our HAP approach differs from prior methods in a number of respects.
First, we do not assume a surface. Rather, we more fundamentally
consider a collection of amphiphilic particles.  The collection of
amphiphiles minimize hydrophobic interactions by sequestering
hydrophobic tails in the form of a bilayer, and the particles' excess
free energy gives rise to an elastic bilayer energy. The second
difference lies in the fluid-interface coupling. Here, the associated
mobility problem~\eqref{eq:stokes} is more complicated than dealing with
a stress boundary condition or diffusive surface force, because the
fluid velocity must be that of a rigid body motion at the particle
surfaces. The HAP model also addresses the existence of multiple phases.
We can vary lipid length, spontaneous curvature, and bending rigidity by
introducing differentiating particle shapes and hydrophobic boundary
conditions (Figure \ref{fig:demixing}). In contrast, continuum theory
deals with multiple phases through additional surface densities that
must then satisfy specialized transport equations~\cite{Lowengrub07,
MikuckiZhou17}. 
%
\begin{wrapfigure}[17]{l}{0.4\textwidth}
\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
\caption{\label{fig:demixing} An initial assembly of small and 
large particles spontaneous segregates into two smaller bodies. }
\end{wrapfigure}
The greatest strength of using HAP to model lipid bilayer membrane is
the ability to form discontinuities (interfacial singularity) from first
physical principle without any artificial manipulation to rearrangement
the interface.
%The ability to form discontinuities is perhaps the HAP method's greatest strength.
For example, using the HAP model to simulate a vesicle under a shear
flow that is strong enough to cause the vesicle membrane to rupture, we
expect the HAP model to capture the reorganization of lipid molecules on
the scales of membrane thickness ($\sim 5$ nm), which is a nearly
impossible task using phase-field or immerse boundary method without
extreme refinement around the membrane and artificial treatment of
reconnection during the topological change of an interface.

### 2020-11-10 NSF2020/Description/preliminarywork.tex
fixing merge conflict
working on background but not done yet

\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
>>>>>>> 6fdd947a0d9a0da241b1d3810791b9a4b58b70cf
%The motion of vesicles in shear flow is an important
%problem in the applied mathematics because simulations can reveal mechanical
%properties of membranes and lead to an enhanced understanding of 
%deformable particle laden flows \cite{Sinha15}. 
%
To implement a vesicle in shear flow in the context of hydrophobic potentials and mobility problem, 
we consider a shear flow in the far-field $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the $x$-axis
(Figure \ref{fig:tanktreading}A).
%
%This field satisfies the linear Stokes system but does not give rise to a rigid motion at the particle interfaces. 
%To have a rigid motion, we change variables $\mathbf{u} = \tilde{\mathbf{u}}+ \mathbf{u}_{\infty}$ and 
%for the new field $\tilde{\mathbf{u}}$ vanishing at infinity we let 
%$\tilde{\mathbf{u}}|_{\partial P_i} = \mathbf{v}_i + \boldsymbol{\omega}_i \times (\mathbf{x} - \mathbf{a}_i)$ 
%where $(\mathbf{v}_i,\boldsymbol{\omega}_i)$ are the unknown translation and angular velocities of the 
%$i$th particle $P_i.$  
%
%\begin{wrapfigure}[17]{l}{0.4\textwidth}
%\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
%\caption{\label{fig:demixing} An initial assembly of small and 
%large particles spontaneous segregates into two smaller bodies. }
%\end{wrapfigure}
The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
vesicle rotates in the clockwise direction. As the rate of rotation increases, the vesicle approaches
a steadily tank-treading ellipse. In Figure \ref{fig:tanktreading}B-D, the solid curves are ellipses fit to the particle centers
and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
and the vesicle diameter is about 14. 
%\todo[inline]{missing units. nm?}
%
\begin{wrapfigure}[12]{r}{0.2\textwidth}
\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
\end{wrapfigure}
%
Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
red and blue curves, yet oscillating in the high-shear rate (yellow) curve.
The tank-treading vesicle elongates and becomes more horizontal 
with an increase in flow rate or 
with a decrease in stiffness (effected by decreasing $\rho = 4$ to $\rho = 2$).

@@

%\begin{wrapfigure}[12]{r}{0.2\textwidth}
%\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
%\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
%\end{wrapfigure}
There are a number of advantages to using our particle based approach.
For one, the HAP theory automatically accounts for the existence of multiple phases. 
For example, we can vary lipid length, spontaneous curvature and bending rigidity 
by introducing differentiating particle shapes and hydrophobic boundary conditions (Figure \ref{fig:demixing}).
Continuum theory deals with multiple phases through additional surface densities that must
then satisfy specialized transport equations \cite{Lowengrub07,MikuckiZhou17}. 
As illustrated in Figure \ref{fig:tanktreading}, the particle
based approach supports inter-leaflet slip, and this can be used to determine inter-leaflet
and in-plane shear viscosities. 
%

>>>>

\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
%The motion of vesicles in shear flow is an important
%problem in the applied mathematics because simulations can reveal mechanical
%properties of membranes and lead to an enhanced understanding of 
%deformable particle laden flows \cite{Sinha15}. 
%
To implement a vesicle in shear flow in the context of hydrophobic
potentials and mobility problem, we consider a shear flow in the
far-field $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the
$x$-axis (Figure \ref{fig:tanktreading}A). As illustrated in Figure
\ref{fig:tanktreading}, the particle based approach supports
inter-leaflet slip, and this can be used to determine inter-leaflet and
in-plane shear viscosities. 
%
%This field satisfies the linear Stokes system but does not give rise to a rigid motion at the particle interfaces. 
%To have a rigid motion, we change variables $\mathbf{u} = \tilde{\mathbf{u}}+ \mathbf{u}_{\infty}$ and 
%for the new field $\tilde{\mathbf{u}}$ vanishing at infinity we let 
%$\tilde{\mathbf{u}}|_{\partial P_i} = \mathbf{v}_i + \boldsymbol{\omega}_i \times (\mathbf{x} - \mathbf{a}_i)$ 
%where $(\mathbf{v}_i,\boldsymbol{\omega}_i)$ are the unknown translation and angular velocities of the 
%$i$th particle $P_i.$  
%
%\begin{wrapfigure}[17]{l}{0.4\textwidth}
%\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
%\caption{\label{fig:demixing} An initial assembly of small and 
%large particles spontaneous segregates into two smaller bodies. }
%\end{wrapfigure}
The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
vesicle rotates in the clockwise direction. As the rate of rotation increases, the vesicle approaches
a steadily tank-treading ellipse. In Figure \ref{fig:tanktreading}B-D, the solid curves are ellipses fit to the particle centers
and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
and the vesicle diameter is about 14. 
%\todo[inline]{missing units. nm?}
%
\begin{wrapfigure}[12]{r}{0.2\textwidth}
\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
\end{wrapfigure}
%
Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
red and blue curves, yet oscillating in the high-shear rate (yellow) curve.
The tank-treading vesicle elongates and becomes more horizontal 
with an increase in flow rate or 
with a decrease in stiffness (effected by decreasing $\rho = 4$ to $\rho = 2$).

@@

%\begin{wrapfigure}[12]{r}{0.2\textwidth}
%\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
%\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
%\end{wrapfigure}
%
